*Supplementary Material 1*

### 2022-06-21 ms/si.Rmd
Add rogues table

acc_table_long <- read_from_cache("acc_table_long", ftol_cache)
con_fossil_calibration_tips <- read_from_cache("con_fossil_calibration_tips", ftol_cache) # nolint
con_fossil_calibrations_for_treepl <- read_from_cache("con_fossil_calibrations_for_treepl", ftol_cache) # nolint
fossil_ferns_all <- read_from_cache("fossil_ferns_all", ftol_cache)
plastome_seqs_combined_filtered <- read_from_cache("plastome_seqs_combined_filtered", ftol_cache) # nolint
plastome_tree <- read_from_cache("plastome_tree", ftol_cache)
plastome_tree_rooted <- read_from_cache("plastome_tree_rooted", ftol_cache)
sanger_accessions_selection <- read_from_cache("sanger_accessions_selection", ftol_cache) # nolint
sanger_con_tree_dated <- read_from_cache("sanger_con_tree_dated", ftol_cache)
sanger_con_tree_rooted <- read_from_cache("sanger_con_tree_rooted", ftol_cache)
sanger_alignment_tbl <- read_from_cache("sanger_alignment_tbl", ftol_cache)
ts_fossil_calibration_tips <- read_from_cache("ts_fossil_calibration_tips", ftol_cache) # nolint

@@

>>>>

acc_table_long <- read_from_cache("acc_table_long", ftol_cache)
con_fossil_calibration_tips <- read_from_cache("con_fossil_calibration_tips", ftol_cache) # nolint
con_fossil_calibrations_for_treepl <- read_from_cache("con_fossil_calibrations_for_treepl", ftol_cache) # nolint
fossil_ferns_all <- read_from_cache("fossil_ferns_all", ftol_cache)
plastome_seqs_combined_filtered <- read_from_cache("plastome_seqs_combined_filtered", ftol_cache) # nolint
plastome_tree <- read_from_cache("plastome_tree", ftol_cache)
plastome_tree_rooted <- read_from_cache("plastome_tree_rooted", ftol_cache)
sanger_accessions_selection <- read_from_cache("sanger_accessions_selection", ftol_cache) # nolint
sanger_con_tree_dated <- read_from_cache("sanger_con_tree_dated", ftol_cache)
sanger_con_tree_rooted <- read_from_cache("sanger_con_tree_rooted", ftol_cache)
sanger_alignment_tbl <- read_from_cache("sanger_alignment_tbl", ftol_cache)
ts_fossil_calibration_tips <- read_from_cache("ts_fossil_calibration_tips", ftol_cache) # nolint
sanger_seqs_rogues_inspected <- read_from_cache(
  "sanger_seqs_rogues_inspected", ftol_cache
)

@@

```{r rogues-make}
rogues_table <-
  sanger_seqs_rogues_inspected %>%
  # FIXME: manually correct one species
  # should delete this after correcting
  # https://github.com/fernphy/ftol/issues/16
  filter(species != "Dryopolystichum_phaeostigma") %>%
  arrange(species, target) %>%
  rename(locus = target)
```

```{r rogues-save, eval = params$doc_type == "doc"}
# Save if rendering to doc
write_csv(rogues_table, result_file(s_table("rogues"), "csv"))
```

**`r s_table("rogues")`**.
GenBank accessions identified as rogues by all-by-all BLAST.
"q_family" is the family of the GenBank query (accession).
"s_family" is the family of the top three best matches (only cases where the top three matches all belong to the same family included).
All accessions in this table were excluded from further analysis.
